### 2023-09-07 Notes/model_assumptions.tex
Reorganized Simulations/ directory. Updated README.

\begin{itemize}
  \item Let $U = \{1, \dots N\}$ be a finite population.
  \item Consider the random variables $(X_i, Y_{1i}, Y_{2i}, \pi_i) 
    \stackrel{\text{ind}}{\sim} F$ for some unknown $F$ for all $i \in U$.
  \item Let $I_i \stackrel{\text{ind}}{\sim} \pi_i$ for $i \in U$ be the 
    sample inclusion indicator.
  \item We assume that $x_i$ is observed throughout the finite population.
  \item However, $(y_{1i}, y_{2i}, \pi_i)$ is only observed if $I_i = 1$.
  \item The goal is to estimate $\theta = E[g(X, Y_1, Y_2)]$ in the population.
  \item The proposed estimator is

  \begin{align}\label{eq:prop}
    \hat \theta_{\text{eff}} 
    &= n^{-1} \sum_{i = 1}^n E[g_i \mid X_i] \nonumber \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{1i}}{\pi_{1+}(X_i)}
      (E[g_i \mid X_i, Y_{1i}] - E[g_i \mid X_i])\nonumber  \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{2i}}{\pi_{2+}(X_i)}
      (E[g_i \mid X_i, Y_{2i}] - E[g_i \mid X_i])\nonumber  \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{1i} R_{2i}}{\pi_{11}(X_i)}
      (g_i - E[g_i \mid X_i, Y_{1i}] - E[g_i \mid X_i, Y_{2i}] + E[g_i \mid X_i])
  \end{align}

@@

  \begin{align*}
    \hat \theta_{\text{eff}} 
    &= n^{-1} \sum_{i = 1}^n E[g_i \mid X_i] \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{1i}}{\pi_{1+}(X_i)}
      (b(X_i, Y_{1i}) - E[g_i \mid X_i]) \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{2i}}{\pi_{2+}(X_i)}
      (a(X_i, Y_{2i}) - E[g_i \mid X_i]) \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{R_{1i} R_{2i}}{\pi_{11}(X_i)}
      (g_i - b_i - a_i + E[g_i \mid X_i]).
  \end{align*}

@@

I have done a lot to explore this area but I have several points of confusion.
The first part recaps what Dr. Fuller and I discussed this past week.

\begin{itemize}
  \item Let $g = E[Y_2]$, and suppose that we know the distribution of $X$ and 
    the covariance structure of $[X, Y_1, Y_2, \pi]$. Then instead of modeling
    the relationship between $X$ and $Y_k$, we can use difference estimators:
    $W_1 \equiv Y_1 - b_1 \tilde X$ and $W_2 = \equiv Y_2 - b_2 \tilde X$, where
    $\tilde X = X - E[X]$.
    To minimize the variance of $W_k$ we can choose the optimal value of $b_k$,
     which is

@@

    Since these values are known, $b_k$ is known. This means that we now have
    the following table:

    \begin{figure}[!ht]
      \centering
      \begin{tabular}{lrr}
        \toprule
         & $W_1$ & $W_2$ \\
         \midrule
        $A_{11}$ & \checkmark & \checkmark \\
        $A_{10}$ & \checkmark & \\
        $A_{01}$ & & \checkmark \\
        $A_{00}$ & & \\
        \bottomrule
      \end{tabular}
    \end{figure}

@@

    \[ 
      \begin{pmatrix}
        x_i \\ e_{1i} \\ e_{2i}
      \end{pmatrix} \stackrel{ind}{\sim}
      N \left(
      \begin{bmatrix}
        0 \\ 0 \\ 0
      \end{bmatrix},
      \begin{bmatrix}
        1 & 0 & 0 \\
        0 & \sigma_{11} & 0 \\ 
        0 & 0 & \sigma_{22}
      \end{bmatrix},
      \right)
    \]

    and define $y_{1i} = x_i + e_{1i}$ and $y_{2i} = x_i + e_{2i}$. Then $b_1 =
    b_2 = 1$. We define $\bar w_k^{(ij)}$ as the mean of $y_k$ in segment
    $A_{ij}$. This means that we have means $\bar w_1^{(11)}$, $\bar
    w_2^{(11)}$, $\bar w_1^{(10)}$, and $\bar w_2^{(01)}$. Let 
    $W = [\bar w_1^{(11)}, \bar w_2^{(11)}, \bar w_1^{(10)}, \bar w_2^{(01)}]'$,
    then for $n_{ij} = |A_{ij}|$, we have

    \[W - M \mu \sim N(\vec 0, V)\]

@@

    \[M = 
      \begin{bmatrix}
        1 & 0 \\
        0 & 1 \\
        1 & 0 \\
        0 & 1 \\
      \end{bmatrix}
      \text{ and }
      V = 
      \begin{bmatrix}
        \frac{\sigma_{11}}{n_{11}} & 0 & 0 & 0 \\
        0 & \frac{\sigma_{22}}{n_{11}} & 0 & 0 \\
        0 & 0 & \frac{\sigma_{11}}{n_{10}} & 0 \\
        0 & 0 & 0 & \frac{\sigma_{22}}{n_{01}} \\
      \end{bmatrix}.
    \]

@@

    \[ \hat \mu = (M' V^{-1} M)^{-1} M' V^{-1} W. \]

  \item If we do the matrix algebra, $V^{-1} = 
    \text{diag}\left(\frac{n_{11}}{\sigma_{11}}, \frac{n_{11}}{\sigma_{22}},
    \frac{n_{10}}{\sigma_{11}}, \frac{n_{01}}{\sigma_{22}}\right)$ and hence,

    {\renewcommand{\arraystretch}{2}
    \begin{equation}\label{eq:wls}
    \hat \mu = 
      \begin{bmatrix}
        \frac{n_{11}\bar w_1^{(11)} + n_{10}\bar w_1^{(10)}}{n_{11} + n_{10}} \\
        \frac{n_{11}\bar w_2^{(11)} + n_{01}\bar w_2^{(01)}}{n_{11} + n_{01}} \\
      \end{bmatrix}
    \end{equation}
    }

@@

    \[
      \begin{pmatrix}
        x_i \\ e_{1i} \\ e_{2i}
      \end{pmatrix} \stackrel{ind}{\sim}
      N \left(
      \begin{bmatrix}
        0 \\ 0 \\ 0
      \end{bmatrix},
      \begin{bmatrix}
        1 & 0 & 0 \\
        0 & 1 & 0 \\ 
        0 & 0 & 1 
      \end{bmatrix},
      \right) \text{ and }
      y_{1i} = x_i + e_{1i}, y_{2i} = x_i + e_{2i}.
    \]

@@

@@

      \item IPW: This computes the survey weighted average of $Y_2$ when both
        $Y_1$ and $Y_2$ are observed.
        \[\hat \theta = \frac{\sum_{i = 1}^n \delta_{1i}\delta_{2i} y_{2i}}
        {\sum_{i = 1}^n \delta_{1i}\delta_{2i}}.\]
      \item Proposed: This is the proposed estimator from Equation~\ref{eq:prop}.
      \item WLS: This is the weighted linear estimator from Equation~\ref{eq:wls}.
        (Note, since $g = E[Y_2]$ this only contains the second element from
        Equation~\ref{eq:wls}.)
    \end{itemize}

    The results are shown in the table below. This simulation was run with the 
    number of observations $n = 1000$ and the Monte Carlo sample size of 
    $B = 1000$.

    \begin{table}[ht!]
      \centering
      \caption{This table shows the estimators of $\theta = E[Y_2]$. The true 
      value of $\theta$ is $0$. The bias column shows the average bias of the 
      estimator and the actual value of $\theta = 0$ across the $B = 1000$ 
      simulations. The SD column shows the average standard deviation across the 
      $B = 1000$ simulations for each algorithm. The Tstat column displays the 
      t-statistic of a t-test comparing the estimator to the actual value. 
      The value of this column is computed via $\frac{\bar{\hat{\theta}} - 
      \theta}{\sqrt{\Var{\hat \theta}/B}}$. The Pval column displays the 
      p-value of the t-statistic.}
      \begin{tabular}[t]{lrrrr}
        \toprule
        Algorithm & Bias & SD & Tstat & Pval\\
        \midrule
        Oracle & -0.001 & 0.045 & -0.953 & 0.170\\
        CC & 0.000 & 0.056 & -0.059 & 0.476\\
        IPW & 0.000 & 0.071 & -0.183 & 0.428\\
        Prop & 0.000 & 0.051 & -0.131 & 0.448\\
        WLS & -0.001 & 0.042 & -0.470 & 0.319\\
        \bottomrule
      \end{tabular}
      \label{tab:res}
    \end{table}

  \item There are a couple things of note from Table~\ref{tab:res}. First, the 
    WLS estimator has a smaller standard error than the Oracle estimator. This 
    seems incorrect. (Please see the next section for questions.) Second, the 
    proposed estimator did not have a similar standard error as the WLS estimator.
    This suggests that it is not optimal.
\end{itemize}

\section*{Questions for Dr. Fuller}

\begin{enumerate}
  \item For the linear estimator I don't think that I am incorporating sampling
    weights. I am a bit confused about how to do this. Should I compute the 
    means $\bar w_{k}^{(ij)}$ using weights according to the sample weights? 
  \item Is it ok for the linear estimator to outperform the oracle estimator?
    This seems odd to me because the oracle estimator seems to contain more 
    information.
  \item On Tuesday, you asked me to compute the linear estimator in terms of 
    means of $Y$ and estimators of $0$. I think that the WLS estimator is the 
    estimator in terms of estimators of $0$ because $y_k - b_k x$ is an 
    estimator of $0$. To transform the estimator into an estimator in terms of
    $Y$, should I write the form in terms of $Y$ instead of $W$?
\end{enumerate}

>>>>

\begin{itemize}
  \item Let $U = \{1, \dots N\}$ be a finite population.
  \item Consider the random variables $(X_i, Y_{1i}, Y_{2i}, \pi_i) 
    \stackrel{\text{ind}}{\sim} F$ for some unknown $F$ for all $i \in U$.
  \item We assume that $x_i$ is observed throughout the finite population.
  \item Let $I_i \stackrel{\text{ind}}{\sim} \pi_i$ for $i \in U$ be the 
    first phase sample inclusion indicator.
  \item If $i \in \{1, \dots, N\}$ is in the first phase sample ($I_i = 1$)
    then $\pi_i$ is observed. 
  \item The second phase sampling indicators are $\delta_{00}$, $\delta_{01}$,
    $\delta_{10}$, and $\delta_{11}$. These mutual exclusive variables encode 
    the following: if both $Y_1$ and $Y_2$ are observed then $\delta_{11} = 1$;
    if $Y_1$ is observed and $Y_2$ is missing then $\delta_{10} = 1$; if $Y_1$
    is missing and $Y_2$ is observed then $\delta_{01} = 1$; and if both $Y_1$
    and $Y_2$ are missing then $\delta_{00} = 1$. (For notational purposes, it
    is sometimes convienent to write $\delta_{1} = \delta_{11} + \delta_{10}$ 
    and $\delta_2 = \delta_{11} + \delta_{01}$. A similar notation will be 
    used for $\pi$. We have $\pi_{1+} = \pi_{11} + \pi_{10}$ and 
    $\pi_{2+} = \pi_{11} + \pi_{01}$.)
  \item All of the sampling indicators were drawn via \textit{Poisson}
    sampling. So the sample size of each category $A_{ij}$ is random. However,
    this does ensure independence between observations.
  \item The goal is to estimate $\theta = E[g(X, Y_1, Y_2)]$ in the population.
  \item The proposed estimator is

  \begin{align}\label{eq:prop}
    \hat \theta_{\text{eff}} 
    &= n^{-1} \sum_{i = 1}^n E[g_i \mid X_i] \nonumber \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{1i}}{\pi_{1+}(X_i)}
      (E[g_i \mid X_i, Y_{1i}] - E[g_i \mid X_i])\nonumber  \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{2i}}{\pi_{2+}(X_i)}
      (E[g_i \mid X_i, Y_{2i}] - E[g_i \mid X_i])\nonumber  \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{1i} \delta_{2i}}{\pi_{11}(X_i)}
      (g_i - E[g_i \mid X_i, Y_{1i}] - E[g_i \mid X_i, Y_{2i}] + E[g_i \mid X_i])
  \end{align}

@@

    \begin{align}\label{eq:propclass}
    \hat \theta_{\text{eff}} 
    &= n^{-1} \sum_{i = 1}^n E[g_i \mid X_i]\nonumber \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{1i}}{\pi_{1+}(X_i)}
      (b(X_i, Y_{1i}) - E[g_i \mid X_i])\nonumber \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{2i}}{\pi_{2+}(X_i)}
      (a(X_i, Y_{2i}) - E[g_i \mid X_i])\nonumber \\ 
    &+ n^{-1} \sum_{i = 1}^n \frac{\delta_{1i} \delta_{2i}}{\pi_{11}(X_i)}
      (g_i - b_i - a_i + E[g_i \mid X_i]).
    \end{align}

@@

The first part recaps what Dr. Fuller and I discussed previously.

\begin{itemize}
  \item Let $g = E[Y_2]$, and suppose that we know the distribution of $X$ and 
    the covariance structure of $[X, Y_1, Y_2, \pi]$. Then instead of modeling
    the relationship between $X$ and $Y_k$, we can use difference estimators:
    $Z_1 \equiv Y_1 - b_1 \tilde X$ and $Z_2 = \equiv Y_2 - b_2 \tilde X$, where
    $\tilde X = X - E[X]$.
    To minimize the variance of $Z_k$ we can choose the optimal value of $b_k$,
     which is

@@

    Since these covariance values are known, $b_k$ is known. This means that we
    now have the following table:

    \begin{figure}[!ht]
      \centering
      \begin{tabular}{lrr}
        \toprule
         & $Z_1$ & $Z_2$ \\
         \midrule
        $A_{11}$ & \checkmark & \checkmark \\
        $A_{10}$ & \checkmark & \\
        $A_{01}$ & & \checkmark \\
        $A_{00}$ & & \\
        \bottomrule
      \end{tabular}
    \end{figure}

@@

    \[ 
      \begin{pmatrix}
        x_i \\ e_{1i} \\ e_{2i}
      \end{pmatrix} \stackrel{ind}{\sim}
      N \left(
      \begin{bmatrix}
        0 \\ 0 \\ 0
      \end{bmatrix},
      \begin{bmatrix}
        1 & 0 & 0 \\
        0 & \sigma_{11} & \sigma_{12} \\ 
        0 & \sigma_{12} & \sigma_{22}
      \end{bmatrix},
      \right)
    \]

    and define $y_{1i} = \theta_1 + x_i + e_{1i}$ and $y_{2i} = \theta_2 + x_i
    + e_{2i}$. Then $b_1 = b_2 = 1$. We define $\bar z_k^{(ij)}$ as the mean of
    $y_k$ in segment $A_{ij}$. This means that we have means $\bar z_1^{(11)}$,
    $\bar z_2^{(11)}$, $\bar z_1^{(10)}$, and $\bar z_2^{(01)}$. Let $W = [\bar
    z_1^{(11)}, \bar z_2^{(11)}, \bar z_1^{(10)}, \bar z_2^{(01)}]'$, then for
    $n_{ij} = |A_{ij}|$, we have

    \[Z - M \mu \sim N(\vec 0, V)\]

@@

    \[M = 
      \begin{bmatrix}
        1 & 0 \\
        0 & 1 \\
        1 & 0 \\
        0 & 1 \\
      \end{bmatrix}
      \text{ and }
      V = 
      \begin{bmatrix}
        \frac{\sigma_{11}}{n_{11}} & \frac{\sigma_{12}}{n_{11}} & 0 & 0 \\
        \frac{\sigma_{12}}{n_{11}} & \frac{\sigma_{22}}{n_{11}} & 0 & 0 \\
        0 & 0 & \frac{\sigma_{11}}{n_{10}} & 0 \\
        0 & 0 & 0 & \frac{\sigma_{22}}{n_{01}} \\
      \end{bmatrix}.
    \]

@@

    \begin{equation}\label{eq:wls}
    \hat \mu = (M' V^{-1} M)^{-1} M' V^{-1} W.
    \end{equation}

@@

    \[
      \begin{pmatrix}
        x_i \\ e_{1i} \\ e_{2i}
      \end{pmatrix} \stackrel{ind}{\sim}
      N \left(
      \begin{bmatrix}
        0 \\ 0 \\ 0
      \end{bmatrix},
      \begin{bmatrix}
        1 & 0 & 0 \\
        0 & 1 & \sigma_{12} \\ 
        0 & \sigma_{12} & 1 
      \end{bmatrix},
      \right) \text{ and }
      y_{1i} = \theta_1 + x_i + e_{1i}, y_{2i} = \theta_2 + x_i + e_{2i}.
    \]

@@

      \item OracleX: This computes the average value of $Y_2 - X$ in 
        all observations (even when $Y_2$ is not supposed to be observed.)
        \[\hat \theta = n^{-1} \sum_{i = 1}^n (y_{2i} - x_i).\]

@@

      \item Proposed: This is the proposed estimator from Equation~\ref{eq:prop}.
      \item WLS: This is the weighted linear estimator from Equation~\ref{eq:wls}.
        Note, since $g = E[Y_2]$ this only contains the second element from
        Equation~\ref{eq:wls}.
    \end{itemize}

    The results are shown in the table below. This simulation was run with the 
    number of observations $n = 1000$ and the Monte Carlo sample size of 
    $B = 3000$.

    \begin{table}[ht!]
      \label{tab:res}
      \caption{This table shows the estimators of $\theta = E[Y_2]$. The true 
        value of $\theta$ is $5$ and the true value of $\sigma_{12} = 0.5$.
        The bias column shows the average bias of the 
      estimator and the actual value of $\theta = 5$ across the $B = 3000$ 
      simulations. The SD column shows the average standard deviation across the 
      $B = 3000$ simulations for each algorithm. The Tstat column displays the 
      t-statistic of a t-test comparing the estimator to the actual value. 
      The value of this column is computed via $\frac{\bar{\hat{\theta}} - 
      \theta}{\sqrt{\Var{\hat \theta}/B}}$. The Pval column displays the 
      p-value of the t-statistic.}
      \centering
      \begin{tabular}[t]{lrrrr}
        \toprule
        Algorithm & Bias & SD & Tstat & Pval\\
        \midrule
        Oracle & 0.001 & 0.044 & 1.546 & 0.061\\
        OracleX & 0.000 & 0.032 & 0.479 & 0.316\\
        CC & 0.002 & 0.058 & 1.549 & 0.061\\
        WLS & 0.001 & 0.040 & 1.207 & 0.114\\
        Prop & 0.002 & 0.051 & 1.918 & 0.028\\
        \bottomrule
      \end{tabular}
    \end{table}

\section*{Computing the Variance by Hand}

Table~\ref{tab:res} demonstrates that the WLS estimator outperforms the 
Oracle estiamator. I was initially confused about why this is the case, but
realized that I could approximate the standard error of both estimators
reasonably well. It turns out that I was able to get reasonable estimates 
for the variance of all of the proposed estimators includeing $\hat
\theta_{prop}$. In this part of the report, I detail my computations and show
how the simulated results are accurate.

\begin{align}\label{eq:varor}
  \Var(\hat \theta_{Oracle}) 
  &= \Var\left(n^{-1} \sum_{i = 1}^n y_{2i}\right) \nonumber \\
  &= n^{-1} \Var(y_{2}) \nonumber \\
  &= n^{-1} (1 + \sigma_{22}) & \text{because $\Var(x) = 1$.}
\end{align}

\begin{align}\label{eq:varorx}
  \Var(\hat \theta_{OracleX}) 
  &= \Var\left(n^{-1} \sum_{i = 1}^n y_{2i} - x_i\right) \nonumber \\
  &= n^{-1} \Var(e_{2}) \nonumber \\
  &= n^{-1} \sigma_{22}.
\end{align}

Using a Taylor expansion,

\begin{align}\label{eq:varcc}
  \Var(\hat \theta_{cc})
  &= \Var\left(\theta_2 + \pi_{2+}^{-1} \left(n^{-1}\sum_{i = 1}^n \delta_{2i} y_{2i}
  - \pi_{2+}\theta_2\right) - \frac{\theta_2 \pi_{2+}}{\pi_{2+}^2} 
  \left(n^{-1} \sum_{i = 1}^n \delta_{2i} - \pi_{2+}\right) + o_p(1)\right)\nonumber  \\
  &\quad (\text{I can add more steps later if necessary.})\\
  &= \frac{1 + \sigma_{22}}{n \pi_{2+}} + o_p(1).
\end{align}

To compute the variance of $\hat \theta_{WLS}$, we have,

\begin{align}\label{eq:varwls}
  \Var(\hat \theta_{WLS})
  &= \Var((M'V^{-1}V)^{-1}M'V^{-1}Z) \nonumber \\ 
  &= E[\Var((M'V^{-1}V)^{-1}M'V^{-1}Z \mid n_1)]\nonumber  \\
  &= E[(M'V^{-1}M)]\\
\end{align}

By Slutky's Theorem, $\Var(\hat \theta_{WLS}) \stackrel{P}{\to} (M'E[V]^{-1}M)^{-1}$.

Finally, we compute the variance for the proposed estimator. First, we
estimate the variance for a similar estimator $\tilde \theta_{prop}$. This
estimator is the same as the proposed estimator except that we assume that 
the estimates from $E[Y_{2i} \mid X, Y_1]$ and $E[Y_{2i} \mid X]$ are 
population coefficients and independent of the rest of the sample. This
could occur if there is a separate sample in which we can estimate these 
expectations. Since the population coefficients of the regression 
$Y = \beta_0 + \beta_1 X$ are

\[\beta_0 = E[Y] - E[X] \Var(X)^{-1} Cov(X'Y) \text{ and } 
\beta_1 = \Var(X)^{-1}\Cov(X, Y),\]

we have that,

\begin{align*}
  E[Y_2 \mid X] &= E[Y_2] - \beta_1 E[X] + \beta_1 x = \theta_2 - x
\end{align*}

and

\begin{align*}
  E[Y_2 \mid X, Y_1] 
  &= \beta_0 + [X, Y_1][\beta_1 \beta_2]' \\ 
  &= E[Y_2] - E[[X, Y_1]] \Var([X, Y_1])^{-1}\Cov([X, Y_1], Y_2) + 
  [X, Y_1]\Var([X, Y_1])^{-1} \Cov([X, Y_1], Y_2) \\ 
  &= \theta_2 + [X, Y_1] \sigma_{11}^{-1} 
  \begin{bmatrix}
    1 + \sigma_{11} & -1 \\ -1 & 1
  \end{bmatrix}
  \begin{bmatrix}
    1 & 1 + \sigma_{12}
  \end{bmatrix} \\
  &= \theta_2 + x \left(\frac{\sigma_{11} - \sigma_{12}}{\sigma_{11}}\right) + 
  y_1 \left(\frac{\sigma_{12}}{\sigma_{11}}\right)\\
  &= \theta_2 + x(1 - \sigma_{12}) + y_1(\sigma_{12}). 
\end{align*}

This means that

\[E[Y_2 \mid X, Y_1] - E[Y_2 \mid X] = \sigma_{12}(y_1 - x) = \sigma_{12} e_1.\]

Hence, whereas for $\theta = E[Y_2]$,

\[\hat \theta_{prop} = n^{-1} \sum_{i = 1}^n \left\{E[Y_2 \mid X] +
    \left(\frac{\delta_{1i}}{\pi_{1+}} - \frac{\delta_{11i}}{\pi_{11}}\right)
    (E[Y_2 \mid X, Y_1] - E[Y_2 \mid X]) + 
    \frac{\delta_{2i}}{\pi_{2+}}(y_{2i} - E[Y_2 \mid X])
\right\}\]

for the similar estimator we have

\[\tilde \theta_{prop} = n^{-1} \sum_{i = 1}^n \left( \theta_2 + x_i + 
    \left(\frac{\delta_{1i}}{\pi_{1+}} - \frac{\delta_{11i}}{\pi_{11}}\right)
    \sigma_{12} e_{1i} + \frac{\delta_{2i}}{\pi_{2+}} (e_{2i}) \right)
\]

This means that

\begin{align*}
  \Var(\tilde \theta_{prop})
  &= n^{-1}\Var\left(x + 
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \sigma_{12} e_{1} + \frac{\delta_{2}}{\pi_{2+}} (e_{2}) \right)\\
  &= n^{-1} \left(\Var(x) + \Var\left(
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \sigma_{12} e_{1}
    \right) + \Var\left( \frac{\delta_{2}}{\pi_{2+}} (e_{2}) \right)\right. \\ 
  &\qquad+ \left.2\Cov\left(
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \sigma_{12} e_{1},
     \frac{\delta_{2}}{\pi_{2+}} (e_{2}) 
    \right) \right)\\
  &\equiv A + B + C + D.
\end{align*}

\begin{align*}
  A &= \Var(x) = 1.
\end{align*}

\begin{align*}
  B &= \sigma_{12}^2 \sigma_{11} \Var\left(
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
  \right)\\
    &=  \sigma_{12}^2 \sigma_{11} \left(\Var(\delta_1 / \pi_{1+}) + 
      \Var(\delta_{11}/\pi_{11}) - 
      2\Cov(\delta_1 / \pi_{1+}, \delta_{11} / \pi_{11}) \right)\\
    &= \sigma_{12}^2 \sigma_{11}(\pi_{1+}^{-1} + \pi_{11}^{-1} - 2 - 2(\pi_{11}
    - \pi_{1+} \pi_{11}) / (\pi_{1+}\pi_{11}))\\
    &= \sigma_{12}^2 \sigma_{11}(\pi_{11}^{-1} - \pi_{1+}^{-1}).
\end{align*}

\begin{align*}
  C &= \Var(\delta_2 e_2 / \pi_{2+})\\
    &= \pi_{2+}^{-2}(\Var(\delta_2)\Var(e_2) + \Var(\delta_2)E[e_2]^2 +
    \Var(e_2)E[\delta_2]^2)\\
    &= \pi_{2+}^{-2} (\pi_{2+}(1 - \pi_{2+}) \sigma_{22} + \sigma_{22}\pi_{2+}^2)\\
    &= \sigma_{22} / \pi_{2+}.
\end{align*}

\begin{align*}
  D &= 2\Cov\left(
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \sigma_{12} e_{1}, \frac{\delta_{2}}{\pi_{2+}} (e_{2}) \right)\\
    &= 2E\left[
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \sigma_{12} e_{1} \frac{\delta_{2}}{\pi_{2+}} (e_{2}) 
    \right] \\ 
    &= 2E\left[
    \left(\frac{\delta_{1}}{\pi_{1+}} - \frac{\delta_{11}}{\pi_{11}}\right)
    \frac{\delta_{2}}{\pi_{2+}}
    \right] \sigma_{12}^2\\
    &= 2E\left[\frac{\delta_{11}}{\pi_{1+}\pi_{2+}} - \frac{\delta_{11}}{\pi_{2+}}
    \right] \sigma_{12}^2\\
    &= 2 \frac{\pi_{11}}{\pi_{2+}} (\pi_{1+}^{-1} - 1) \sigma_{12}^2.
\end{align*}

Hence,

\begin{equation}\label{eq:varprop}
\Var(\tilde \theta_{prop}) = n^{-1}(1 +
  \sigma_{12}^2\sigma_{11}(\pi_{11}^{-1} - \pi_{1+}^{-1}) + \sigma_{22}
  \pi_{2+}^{-1} 2\sigma_{12}^2 (\pi_{1+}^{-1} - 1) \pi_{11}/ \pi_{2+}).
\end{equation}

Since $\hat \beta - \beta = O(n)$ from Theorem 2.2.1 of \cite{fuller2009sampling}, 
$\Var(\hat \theta_{prop}) \to \Var(\tilde \theta_{prop})$. (I think that 
I also need to show that the dependency between the estimated 
coefficients and the observed data is bounded and that this bound goes 
to zero as the sample size increases.)

These estimated variances are almost exactly in line with the estimated
standard deviations from the simulation study. With values of $n = 1000$,
$\sigma_{11} = 1$, $\sigma_{22} = 1$, $\sigma_{12} = 0.5$, $\theta_2 = 5$,
$\pi_{11} = 0.4$, $\pi_{10} = 0.2$, $\pi_{01} = 0.2$, and $\pi_{00} = 0.2$
the standard deviations from the previous calculations and from the Monte Carlo
simulation are listed in the Table~\ref{tab:calmc}:

\begin{table}[!ht]
  \centering
  \label{tab:calmc}
  \caption{This table compares the calculated and estimated standard 
  errors for each of the algorithms listed. The calculated values are 
  computed as the square root of the variance derived in the previous 
  section. We use Equations~\ref{eq:varor}, \ref{eq:varorx}, \ref{eq:varcc}
  \ref{eq:varwls}, and \ref{eq:varprop} to calculate the variance of 
  Oracle, OracleX, CC, WLS, and Prop respectively and then take the square
  root of the answer. For the estimated standard error, we take the 
  standard deviation of the $B$ estimators for each algorithm.}
  \begin{tabular}{lrr}
    \toprule
    Algorithm & Calculated Standard Error & Estimated Standard Error \\
    \midrule
    Oracle  & 0.045 & 0.044 \\
    OracleX & 0.032 & 0.032 \\
    CC      & 0.058 & 0.058 \\
    WLS     & 0.040 & 0.040 \\
    Prop    & 0.056 & 0.051 \\
    \bottomrule
  \end{tabular}
\end{table}

\section*{Next Steps}

\begin{itemize}
  \item[1.] Since we have a way to estimate the variance, the goal is still 
    to find the optimal $a$ and $b$ for Equation~\ref{eq:propclass}.
\end{itemize}

\printbibliography
